---
output:
  md_document:
    variant: markdown_github
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![CRAN Version](http://www.r-pkg.org/badges/version/spacyr)](http://cran.r-project.org/package=spacyr) ![Downloads](http://cranlogs.r-pkg.org/badges/spacyr) [![Travis-CI Build Status](https://travis-ci.org/kbenoit/spacyr.svg?branch=master)](https://travis-ci.org/kbenoit/spacyr) [![Appveyor Build status](https://ci.appveyor.com/api/projects/status/jqt2atp1wqtxy5xd/branch/master?svg=true)](https://ci.appveyor.com/project/kbenoit/spacyr/branch/master) [![codecov.io](https://codecov.io/github/kbenoit/spacyr/spacyr.svg?branch=master)](https://codecov.io/github/kbenoit/spacyr/coverage.svg?branch=master)


# spacyr: an R wrapper for spaCy

This package is an R wrapper to the spaCy "industrial strength natural language processing" Python library from http://spacy.io.

### Prerequisites

1.  Python (> 2.7 or 3) must be installed on your system.  

    **(Windows only)**  If you have not yet installed Python,  Download and install [Python for Windows](https://www.python.org/downloads/windows/).  We recommend the latest 2.7.x release (currently 2.7.13).  During the installation process, be sure to scroll down in the installation option window and find the "Add Python.exe to Path", and click on the small red "x." 

2.  A C++ compiler must be installed on your system.  

    * **(Mac only)** Install XTools.  Either get the full XTools from the App Store, or install the command-line XTools using this command from the Terminal:
    
        ```{bash, eval = FALSE}
        xcode-select --install
        ```
    
    * **(Windows only)** Install the [Rtools](https://CRAN.R-project.org/bin/windows/Rtools/) software available 
    from CRAN
    
        You will also need to install the [Microsoft Visual C++ Compiler for Python 2.7](http://aka.ms/vcpython27).
        
        In addition to have `spaCy` on your system, you need to have `libpython` package installed in your Python. If `libpython` is available for `pip` install for your version of Python, you can just type:

        ```{bash, eval = FALSE}
        pip install libpython
        ```

        or for conda Python:
        ```{bash, eval = FALSE}
        conda install -c anaconda libpython=2.0
        ```
    
3.  You will need to install spaCy. 

    Install spaCy and the English language model using these commands at the command line:  
    ```{bash, eval = FALSE}
    pip install -U spacy
    python -m spacy download en
    ```

    Test your installation at the command line using:  

    ```{bash, eval = FALSE}
    python -c "import spacy; spacy.load('en'); print('OK')"
    ```
    There are alternative methods of installing spaCy, especially if you have installed a different Python (e.g. through Anaconda). Full installation instructions are available from the [spaCy page ](http://spacy.io/docs/).


4.  Installing the **spacyr** R package:

    This needs an environment variable set to the location of your Python executable, and then you need to install the package from source.  Note that depending on your operating system and Python installation, the first command might be slightly different.
    
    ```{r, eval = FALSE}
    Sys.setenv(SPACY_PYTHON="/usr/local/bin/python")
    devtools::install_github("kbenoit/spacyr")
    ```

If these steps do not work, see [Installation Problems](#installproblems) below.

## Examples

The `spacy_parse()` function calls spaCy to both tokenize and tag the texts. In addition, it provides a functionalities of dependency parsing and named entity recognition. The function returns a `data.table` of the results. The approach to tokenizing taken by spaCy is inclusive: it includes all tokens without restrictions.  The default method for `tag()` is the [Google tagset for parts-of-speech](https://github.com/slavpetrov/universal-pos-tags).

```{r}
require(spacyr)
# start a python process and initialize spaCy in it.
# it takes several seconds for initialization.
spacy_initialize()

txt <- c(fastest = "spaCy excells at large-scale information extraction tasks. It is written from the ground up in carefully memory-managed Cython. Independent research has confirmed that spaCy is the fastest in the world. If your application needs to process entire web dumps, spaCy is the library you want to be using.",
         getdone = "spaCy is designed to help you do real work — to build real products, or gather real insights. The library respects your time, and tries to avoid wasting it. It is easy to install, and its API is simple and productive. I like to think of spaCy as the Ruby on Rails of Natural Language Processing.")

# process documents and obtain a data.table
parsedtxt <- spacy_parse(txt)
head(parsedtxt)
```

By default, `spacy_parse()` conduct tokenization and part-of-speech (POS) tagging. spacyr provides two tagsets, coarse-grained [Google](https://github.com/slavpetrov/universal-pos-tags) tagsets and finer-grained [Penn Treebank](https://www.ling.upenn.edu/courses/Fall_2003/ling001/penn_treebank_pos.html) tagsets. The `google` or `penn` field in the data.table corresponds to each of these tagsets.


Many of the standard methods from [**quanteda**](http://githiub.com/kbenoit/quanteda) work on the new tagged token objects:
```{r}
require(quanteda, warn.conflicts = FALSE, quietly = TRUE)
docnames(parsedtxt)
ndoc(parsedtxt)
ntoken(parsedtxt)
ntype(parsedtxt)
```

### Document processing with addiitonal features

The following codes conduct more detailed document processing, including dependency parsing and named entitiy recognition.

```{r}
results_detailed <- spacy_parse(txt,
                                pos_tag = TRUE,
                                named_entity = TRUE,
                                dependency = TRUE)
head(results_detailed, 30)
```

### Use German language model

In default, `spacyr` load an English language model in spacy, but you also can load a German language model instead by specifying `lang` option when `spacy_initialize` is called. 

```{r}
spacy_initialize(lang = 'de')

txt_german = c(R = "R ist eine freie Programmiersprache für statistische Berechnungen und Grafiken. Sie wurde von Statistikern für Anwender mit statistischen Aufgaben entwickelt. Die Syntax orientiert sich an der Programmiersprache S, mit der R weitgehend kompatibel ist, und die Semantik an Scheme. Als Standarddistribution kommt R mit einem Interpreter als Kommandozeilenumgebung mit rudimentären grafischen Schaltflächen. So ist R auf vielen Plattformen verfügbar; die Umgebung wird von den Entwicklern ausdrücklich ebenfalls als R bezeichnet. R ist Teil des GNU-Projekts.",
               python = "Python ist eine universelle, üblicherweise interpretierte höhere Programmiersprache. Sie will einen gut lesbaren, knappen Programmierstil fördern. So wird beispielsweise der Code nicht durch geschweifte Klammern, sondern durch Einrückungen strukturiert.")
results_german <- spacy_parse(txt_german,
                                pos_tag = TRUE,
                                named_entity = TRUE,
                                dependency = TRUE)
head(results_german, 30)
```
The German language model has to be installed (`python -m spacy.en.download all`) before you call `spacy_initialize`.

### When you finish

A background process of python is initiated when you ran `spacy_initialize`. Because of the size of English language module of `spaCy`, this takes up a lot of memory (typically 1.5GB). When you do not need the python connection any longer, you can finalize the python (and terminate terminate the process) by running `spacy_finalize()` function.

```{r, eval = FALSE}
spacy_finalize()
```


## <a name="installproblems"></a>Installation Problems

### macOS using Homebrew (or other) versions of Python

If you installed a Python other than the system default and installed spaCy on that Python, then you will need to set the path to the Python executable with spaCy and build `spacyr`. In order to check whether this could be an issue, check the versions of Pythons in Terminal and R.

Open a Terminal window, and type
```
$ python --version; which python
```
and in R, enter following
```{r}
system('python --version; which python')
```
If the outputs are different, loading spaCy is likely to fail as the python executable the `spacyr` calls is different from the version of python spaCy is intalled.

To resolve the issue, you can alter an environmental variable and then reinstall `spacyr`. Suppose that your python with spaCy is  `/usr/local/bin/python`, run the following:
```{r, eval = FALSE}
Sys.setenv(SPACY_PYTHON="/usr/local/bin/python")
devtools::install_github("kbenoit/spacyr")
```


### Multiple Python executables in your system 

If you have multiple python executables in your system, you should be able to specify the Python path using the same method described above, which is to set an enviromental variable `SPACY_PYTHON`.  Example:

```{r, eval = FALSE}
Sys.setenv(SPACY_PYTHON = "C:/Users/***/Anaconda2/python.exe")
devtools::install_github("kbenoit/spacyr")
```

If this installation still fails, you can try our reticulate branch of `spacyr` package. In the back end, it uses [`reticulate`](https://github.com/rstudio/reticulate) package. This version works smoothly python 3.x in our test. There reticualte branch is available [here](https://github.com/kbenoit/spacyr/tree/dev_reticulate).

## Comments and feedback

We welcome your comments and feedback.  Please file issues on the [issues](https://github.com/kbenoit/spacyr/issues) page, and/or send us comments at kbenoit@lse.ac.uk and A.Matsuo@lse.ac.uk.
