---
output:
  md_document:
    variant: markdown_github
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![CRAN Version](http://www.r-pkg.org/badges/version/spacyr)](http://cran.r-project.org/package=spacyr) ![Downloads](http://cranlogs.r-pkg.org/badges/spacyr) [![Travis-CI Build Status](https://travis-ci.org/kbenoit/spacyr.svg?branch=master)](https://travis-ci.org/kbenoit/spacyr) [![codecov.io](https://codecov.io/github/kbenoit/spacyr/spacyr.svg?branch=master)](https://codecov.io/github/kbenoit/spacyr/coverage.svg?branch=master)

(note: the Travis build fails because our script does not install spaCy and the English language files - once these are installed, it passes the R Check.)

# spacyr: an R wrapper for spaCy

This package is an R wrapper to the spaCy "industrial strength natural language processing" Python library from http://spacy.io.

### Prerequisites

1.  Python (> 2.7 or 3) must be installed on your system.  

2.  spaCy must be installed on your system.  Follow [these instructions](http://spacy.io/docs/). 

    Installation on Windows:  
    a)  (If you have not yet installed Python:)  Download and install [Python for Windows](https://www.python.org/downloads/windows/).  We recommend the 2.7.12, using (if appropriate) the Windows x86-64 MSI installer.  During the installation process, be sure to scroll down in the installation option window and find the "Add Python.exe to Path", and click on the small red "x."  
    b)  Install spaCy and the English language model using these commands at the command line:  
        ```
        pip install -U spacy
        python -m spacy.en.download
        ```
        For alternative installations or troubleshooting, see the [spaCy docs](https://spacy.io/docs/).  
    c)  Test your installation at the command line using:  
        ```
        python -c "import spacy; spacy.load('en'); print('OK')"
        ```

3.  You need (of course) to install this package:  
    ```{r, eval = FALSE}
    devtools::install_github("kbenoit/spacyr")
    ```


### Examples

The `spacy_parse()` function calls spaCy to both tokenize and tag the texts. In addition, it provides a functionalities of dependency parsing and named entity recognition. The function returns a `data.table` of the results. The approach to tokenizing taken by spaCy is inclusive: it includes all tokens without restrictions.  The default method for `tag()` is the [Google tagset for parts-of-speech](https://github.com/slavpetrov/universal-pos-tags).

```{r}
require(spacyr)
# start a python process and initialize spaCy in it.
# it takes several seconds for initialization.
spacy_initialize()

# process documents and obtain a data.table
head(data_sentences)
results <- spacy_parse(data_sentences[1:6])
head(results)
```

By default, `spacy_parse()` conduct tokenization and part-of-speech (POS) tagging. spacyr provides two tagsets, coarse-grained [Google](https://github.com/slavpetrov/universal-pos-tags) tagsets and finer-grained [Penn Treebank](https://www.ling.upenn.edu/courses/Fall_2003/ling001/penn_treebank_pos.html) tagsets. The `google` or `penn` field in the data.table corresponds to each of these tagsets.


The package spacyr works nicely with quanteda. The fist step is to generate a tokenized texts object from the results of `spacy_parse()`. 
```{r}
taggedsents <- tokens_tags_out(results, tagset = "penn")
taggedsents
```


Note that while the printed structure appears to append the token and its tag, in fact the structure of the object records these separately:
```{r}
str(taggedsents)
```
This object has the identical structure of quanteda's tokenizedText objects with an additional attribute of tags and will work with methods applied to tokenizedText in quanteda. 

To get a summary of the parts of speech for each document, use the data.frame returned by the `summary()` method for this new object class:
```{r}
summary(taggedsents)
```


Many of the standard methods from [**quanteda**](http://githiub.com/kbenoit/quanteda) work on the new tagged token objects:
```{r}
docnames(taggedsents)
ndoc(taggedsents)
ntoken(taggedsents)
ntype(taggedsents)
```

### Document processing with addiitonal features

The following codes conduct more detailed document processing, including dependency parsing and named entitiy recognition.

```{r}
results_detailed <- spacy_parse(data_sentences[1:6], 
                                pos_tag = TRUE,
                                named_entity = TRUE,
                                dependency = TRUE)
head(results_detailed)
```
When a named entity recognition was conducted the list of all named entities are provided with:

```{r}
all_named_entities(results_detailed)
```


#### Support of hashed tokens class of quanteda

Recent versions of quanteda provides a new class of object called `tokens`. The spacyr package provides a support for this new class.
```{r}
results_hashed <- spacy_parse(data_sentences[1:6], 
                              hash_tokens = TRUE)
head(results_hashed)
taggedsents_hashed <- tokens_tags_out(results_hashed)
str(taggedsents_hashed)
```


## Notes for Mac Users using Homebrew (or other) Version of Python

If you install Python other than the system default and installed spaCy on that Python, you might have to reinstall `rPython` to re-set the python path. In order to check whether this is an issue, check the versions of Pythons in Terminal and R. 

In Terminal, type
```
$ python --version
```
and in R, enter following
```{r}
library(rPython)
python.exec("import platform\nprint(platform.python_version())")
```
If the outputs are different, loading spaCy is likely to fail as the python executable the R system calls is different from the version of python spaCy is intalled.

To resolve the issue please follow the step. Open R *from Terminal* (just enter `R`), then reinstall rPython from source by entering
```{r, eval = FALSE}
install.packages("rPython", type = "source")
```
then execute the R-commands above again to check the version of Python calling from rPython.



## Comments and feedback

We welcome your comments and feedback.  Please file issues on the issues page, and/or send me comments at kbenoit@lse.ac.uk.

Plans moving ahead include finding much more efficient methods of calling spaCy from R than [the current use of `system2()`](https://github.com/kbenoit/spacyr/blob/master/R/tag.R#L71).


