---
output:
  md_document:
    variant: markdown_github
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![CRAN Version](http://www.r-pkg.org/badges/version/spacyr)](http://cran.r-project.org/package=spacyr) ![Downloads](http://cranlogs.r-pkg.org/badges/spacyr) [![Travis-CI Build Status](https://travis-ci.org/kbenoit/spacyr.svg?branch=master)](https://travis-ci.org/kbenoit/spacyr) [![codecov.io](https://codecov.io/github/kbenoit/spacyr/spacyr.svg?branch=master)](https://codecov.io/github/kbenoit/spacyr/coverage.svg?branch=master)

# spacyr: an R wrapper for spaCy

This package is an R wrapper to the spaCy "industrial strength natural language processing" library from http://spacy.io.

### Prerequisites

1.  Python must be installed on your system.  

2.  spaCy must be installed on your system.  Follow [these instructions](http://spacy.io/docs/).

3.  You need (of course) to install this package:  
    ```{r, eval = FALSE}
    devtools::install_github("kbenoit/spacyr")
    ```


### Examples

```{r, eval = FALSE}
require(spacyr)

# coming soon
```


## Comments and feedback

We welcome your comments and feedback.  Please file issues on the issues page, and/or send me comments at kbenoit@lse.ac.uk.


