---
output:
  md_document:
    variant: markdown_github
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![CRAN Version](https://www.r-pkg.org/badges/version/spacyr)](https://CRAN.R-project.org/package=spacyr) ![Downloads](https://cranlogs.r-pkg.org/badges/spacyr) [![Travis-CI Build Status](https://travis-ci.org/kbenoit/spacyr.svg?branch=master)](https://travis-ci.org/kbenoit/spacyr) [![Appveyor Build status](https://ci.appveyor.com/api/projects/status/jqt2atp1wqtxy5xd/branch/master?svg=true)](https://ci.appveyor.com/project/kbenoit/spacyr/branch/master) [![codecov.io](https://codecov.io/github/kbenoit/spacyr/coverage.svg?branch=master)][1]

[1]: https://codecov.io/gh/kbenoit/spacyr/branch/master


# spacyr: an R wrapper for spaCy

This package is an R wrapper to the spaCy "industrial strength natural language processing" Python library from http://spacy.io.

## Installing the package

1.  Install or update Python on your system.  

    macOS and Linux typically come with Python installed, although you may wish to install a newer or different version from https://www.python.org/downloads/.
    
    **Windows only:**  If you have not yet installed Python,  Download and install [Python for Windows](https://www.python.org/downloads/windows/).  We recommend using Python 3, although the Python 2.7.x also works.  During the installation process, be sure to scroll down in the installation option window and find the "Add Python.exe to Path", and click on the small red "x." 

    For the installation of `spaCy` and **spacyr** in macOS (in homebrew and for the default Python) and Windows you can find more detailed instructions for a [Mac OS X Installation](inst/docs/MAC.md) and [Windows Installation](inst/docs/WINDOWS.md).
    
2.  Install additional command-line compiler tools.

    * Windows:
        - Install [Virtual Studio Express 2015]([here](https://www.visualstudio.com/post-download-vs/?sku=xdesk&clcid=0x409&telem=ga#).
        - Install [RTools](https://cran.r-project.org/bin/windows/Rtools/).
        
    * macOS:
        -  Either install XCode from the App Store, or an abbreviated version using the following from Terminal:
           ```{bash, eval = FALSE}
           xcode-select --install
           ```
           
    * Linux: no additional tools are required.


3.  Install spaCy. 

    Installation instructions for spaCy are available [from spacy.io](https://spacy.io/docs/usage/).  In short, once Python is installed on your system:
    ```{bash, eval = FALSE}
    pip install -U spacy
    python -m spacy download en
    ```

    You can test your installation at the command line using:  

    ```{bash, eval = FALSE}
    python -c "import spacy; spacy.load('en'); print('OK')"
    ```
    
    Additional instructions are available from the spaCy website for installing using a [`virtualenv`](https://spacy.io/docs/usage/#pip) or an [Anaconda](https://spacy.io/docs/usage/#conda) installation. 
    
4.  Installing the **spacyr** R package:

    To install the latest package from source, you can simply run the following.
    
    ```{r, eval = FALSE}
    devtools::install_github("kbenoit/spacyr")
    ```
    
    **Coming soon**:  Installation from CRAN will be possible using standard methods.

## <a name="multiplepythons"></a>Multiple Python executables in your system 

If you have multiple Python executables in your systems (for instance if you are a macOS user and have installed Python 3, you will also have the system-installed Python 2.7.x), then the `spacy_initialize()` function will check whether each of them have spaCy installed or not.  To save the time for this checking, you can specify the particular python when initializing spaCy by executing `spacy_initialize()`.  Suppose that your python with spaCy is `/usr/local/bin/python`, run the following:
```{r, eval = FALSE}
library(spacyr)
spacy_initialize(python_executable = "/usr/local/bin/python")
```


## Examples

When initializing spaCy, you need to set the python path if in your system, spaCy is installed in a Python which is not the system default. A detailed discussion about it is found in [Multiple Pythons](#multiplepythons) below.

```{r}
require(spacyr)
# start a python process and initialize spaCy in it.
# it takes several seconds for initialization.
# spacyr attempts to find python with spaCy
spacy_initialize()
```

The `spacy_parse()` function calls spaCy to both tokenize and tag the texts. In addition, it provides a functionalities of dependency parsing and named entity recognition. The function returns a `data.frame` of the results. The approach to tokenizing taken by spaCy is inclusive: it includes all tokens without restrictions.  The `pos` field returned is the [Universal tagset for parts-of-speech](http://universaldependencies.org/u/pos/all.html).

```{r}

txt <- c(d1 = "spaCy excels at large-scale information extraction tasks.",
         d2 = "Mr. Smith goes to North Carolina.")

# process documents and obtain a data.table
parsedtxt <- spacy_parse(txt)
parsedtxt
```

By default, `spacy_parse()` conducts tokenization and part-of-speech (POS) tagging, and returns lemmas and entities.  **spacyr** provides two tagsets, the Universal tagset (`pos`) and the finer-grained tags defined for each language model.  For English, this is the [OntoNotes 5 version of the Penn Treebank tag set](https://spacy.io/docs/usage/pos-tagging#pos-tagging-english).
```{r}
spacy_parse(txt, tag = TRUE, entity = FALSE, lemma = FALSE)
```



Some of the token- and type-related standard methods from [**quanteda**](http://githiub.com/kbenoit/quanteda) also work on the new tagged token objects:
```{r}
require(quanteda, warn.conflicts = FALSE, quietly = TRUE)
docnames(parsedtxt)
ndoc(parsedtxt)
ntoken(parsedtxt)
ntype(parsedtxt)
```

### Extracting entities

**spacyr** can extract entities, either named or ["extended"](https://spacy.io/docs/usage/entity-recognition#entity-types).
```{r}
entity_extract(parsedtxt)
```

```{r}
entity_extract(parsedtxt, type = "all")
```

Or, convert multi-word entities into single "tokens":
```{r}
entity_consolidate(parsedtxt)
```


### Dependency parsing

Detailed parsing of syntactic dependencies is possible with the `dependency = TRUE` option:
```{r}
spacy_parse(txt, dependency = TRUE, lemma = FALSE, pos = FALSE)
```


### Using other language models

By default, **spacyr** loads an English language model in spacy, but you also can load a German language model (or others) instead by specifying `model` option when calling `spacy_initialize()`. 

```{r}
## first finalize the spacy if it's loaded
spacy_finalize()
spacy_initialize(model = "de")

txt_german <- c(R = "R ist eine freie Programmiersprache für statistische Berechnungen und Grafiken. Sie wurde von Statistikern für Anwender mit statistischen Aufgaben entwickelt.",
               python = "Python ist eine universelle, üblicherweise interpretierte höhere Programmiersprache. Sie will einen gut lesbaren, knappen Programmierstil fördern.")
results_german <- spacy_parse(txt_german, dependency = TRUE, tag = TRUE)
results_german
```
Note that the additional language models must first be installed in spaCy.  The German language model can be installed (`python -m spacy download de`) before you call `spacy_initialize()`.

### When you finish

A background process of spaCy is initiated when you ran `spacy_initialize()`. Because of the size of language models of spaCy, this takes up a lot of memory (typically 1.5GB). When you do not need the Python connection any longer, you can finalize the python connection (and terminate the process) by calling the `spacy_finalize()` function.

```{r, eval = FALSE}
spacy_finalize()
```
By calling `spacy_initialize()` again, you can restart the backend spaCy.



## Comments and feedback

We welcome your comments and feedback.  Please file issues on the [issues](https://github.com/kbenoit/spacyr/issues) page, and/or send us comments at kbenoit@lse.ac.uk and A.Matsuo@lse.ac.uk.
