---
output:
  md_document:
    variant: markdown_github
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![CRAN Version](http://www.r-pkg.org/badges/version/spacyr)](http://cran.r-project.org/package=spacyr) ![Downloads](http://cranlogs.r-pkg.org/badges/spacyr) [![Travis-CI Build Status](https://travis-ci.org/kbenoit/spacyr.svg?branch=master)](https://travis-ci.org/kbenoit/spacyr) [![Appveyor Build status](https://ci.appveyor.com/api/projects/status/jqt2atp1wqtxy5xd/branch/master?svg=true)](https://ci.appveyor.com/project/kbenoit/spacyr/branch/master) [![codecov.io](https://codecov.io/github/kbenoit/spacyr/spacyr.svg?branch=master)](https://codecov.io/github/kbenoit/spacyr/coverage.svg?branch=master)


# spacyr: an R wrapper for spaCy

This package is an R wrapper to the spaCy "industrial strength natural language processing" Python library from http://spacy.io.

### Prerequisites

1.  Python (> 2.7 or 3) must be installed on your system.  

2.  spaCy must be installed on your system.  Follow [these instructions](http://spacy.io/docs/).

    Installation on Windows:  
    a)  (If you have not yet installed Python:)  Download and install [Python for Windows](https://www.python.org/downloads/windows/).  We recommend the latest 2.7.x release (currently 2.7.13).  During the installation process, be sure to scroll down in the installation option window and find the "Add Python.exe to Path", and click on the small red "x." 
    
    b)  You will also need to install the [Microsoft Visual C++ Compiler for Python 2.7](http://aka.ms/vcpython27).
    
    c)  Install spaCy and the English language model using these commands at the command line:  
        ```
        pip install -U spacy
        python -m spacy.en.download
        ```
        For alternative installations or troubleshooting, see the [spaCy docs](https://spacy.io/docs/).  
        
        Depending on your system, you may be prompted to install additional components, after which you will need to re-run the `pip install -U spacy` command.  For instance, you may need to install the .NET Framework 3.5.
        
    d)  Test your installation at the command line using:  
        ```
        python -c "import spacy; spacy.load('en'); print('OK')"
        ```

3.  You need (of course) to install this package:  
    ```{r, eval = FALSE}
    devtools::install_github("kbenoit/spacyr")
    ```


### Examples

The `spacy_parse()` function calls spaCy to both tokenize and tag the texts. In addition, it provides a functionalities of dependency parsing and named entity recognition. The function returns a `data.table` of the results. The approach to tokenizing taken by spaCy is inclusive: it includes all tokens without restrictions.  The default method for `tag()` is the [Google tagset for parts-of-speech](https://github.com/slavpetrov/universal-pos-tags).

```{r}
require(spacyr)
# start a python process and initialize spaCy in it.
# it takes several seconds for initialization.
spacy_initialize()

txt <- c(fastest = "spaCy excells at large-scale information extraction tasks. It is written from the ground up in carefully memory-managed Cython. Independent research has confirmed that spaCy is the fastest in the world. If your application needs to process entire web dumps, spaCy is the library you want to be using.",
         getdone = "spaCy is designed to help you do real work — to build real products, or gather real insights. The library respects your time, and tries to avoid wasting it. It is easy to install, and its API is simple and productive. I like to think of spaCy as the Ruby on Rails of Natural Language Processing.")

# process documents and obtain a data.table
parsedtxt <- spacy_parse(txt)
head(parsedtxt)
```

By default, `spacy_parse()` conduct tokenization and part-of-speech (POS) tagging. spacyr provides two tagsets, coarse-grained [Google](https://github.com/slavpetrov/universal-pos-tags) tagsets and finer-grained [Penn Treebank](https://www.ling.upenn.edu/courses/Fall_2003/ling001/penn_treebank_pos.html) tagsets. The `google` or `penn` field in the data.table corresponds to each of these tagsets.


Many of the standard methods from [**quanteda**](http://githiub.com/kbenoit/quanteda) work on the new tagged token objects:
```{r}
require(quanteda, warn.conflicts = FALSE, quietly = TRUE)
docnames(parsedtxt)
ndoc(parsedtxt)
ntoken(parsedtxt)
ntype(parsedtxt)
```

### Document processing with addiitonal features

The following codes conduct more detailed document processing, including dependency parsing and named entitiy recognition.

```{r}
results_detailed <- spacy_parse(txt,
                                pos_tag = TRUE,
                                named_entity = TRUE,
                                dependency = TRUE)
head(results_detailed, 30)
```

## When you finish

A background process of python is initiated when you ran `spacy_initialize`. Because of the size of English language module of `spaCy`, this takes up a lot of memory (typically 1.5GB). When you do not need the python connection any longer, you can finalize the python (and terminate terminate the process) by running `spacy_finalize()` function.

```{r}
spacy_finalize()
```


## Notes for Mac Users using Homebrew (or other) Version of Python

If you install Python other than the system default and installed spaCy on that Python, you need to set the path to the python executable with spaCy and build `spacyr`. In order to check whether this could be an issue, check the versions of Pythons in Terminal and R.

Open a Terminal window, and type
```
$ python --version; which python
```
and in R, enter following
```{r}
system('python --version; which python')
```
If the outputs are different, loading spaCy is likely to fail as the python executable the `spacyr` calls is different from the version of python spaCy is intalled.

To resolve the issue, you can alter an environmental variable and then reinstall `spacyr`. Suppose that your python with spaCy is  `/usr/local/bin/python`, run the following:
```{r, eval = FALSE}
Sys.setenv(SPACY_PYTHON="/usr/local/bin/python")
devtools::install_github("kbenoit/spacyr")
```

## Comments and feedback

We welcome your comments and feedback.  Please file issues on the issues page, and/or send us comments at kbenoit@lse.ac.uk and A.Matsuo@lse.ac.uk.
