---
output:
  md_document:
    variant: markdown_github
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "##",
  fig.path = "README-"
)
```

[![CRAN Version](https://www.r-pkg.org/badges/version/spacyr)](https://CRAN.R-project.org/package=spacyr) ![Downloads](https://cranlogs.r-pkg.org/badges/spacyr) [![Travis-CI Build Status](https://travis-ci.org/kbenoit/spacyr.svg?branch=master)](https://travis-ci.org/kbenoit/spacyr) [![Appveyor Build status](https://ci.appveyor.com/api/projects/status/jqt2atp1wqtxy5xd/branch/master?svg=true)](https://ci.appveyor.com/project/kbenoit/spacyr/branch/master) [![codecov.io](https://codecov.io/github/kbenoit/spacyr/coverage.svg?branch=master)][1]

[1]: https://codecov.io/gh/kbenoit/spacyr/branch/master


# spacyr: an R wrapper for spaCy

This package is an R wrapper to the spaCy "industrial strength natural language processing" Python library from http://spacy.io.

## Installing the package

1.  Install or update Python on your system.  

    macOS and Linux typically come with Python installed, although you may wish to install a newer or different version from https://www.python.org/downloads/.
    
    **Windows only:**  If you have not yet installed Python,  Download and install [Python for Windows](https://www.python.org/downloads/windows/).  We recommend using Python 3, although the Python 2.7.x also works.  During the installation process, be sure to scroll down in the installation option window and find the "Add Python.exe to Path", and click on the small red "x." 

    For the installation of `spaCy` and **spacyr** in macOS (in homebrew and for the default Python) and Windows you can find more detailed instructions for a [Mac OS X Installation](inst/doc/MAC.md) and [Windows Installation](inst/doc/WINDOWS.md).
    
2.  Install additional command-line compiler tools.

    * Windows:
        - Install [Virtual Studio Express 2015]([here](https://www.visualstudio.com/post-download-vs/?sku=xdesk&clcid=0x409&telem=ga#).
        - Install [RTools](https://cran.r-project.org/bin/windows/Rtools/).
        
    * macOS:
    
    Either install XCode from the App Store, or an abbreviated version using the following from Terminal:
    ```{bash, eval = FALSE}
    xcode-select --install
    ```
           
    * Linux: no additional tools are required.


3.  Install spaCy. 

    Installation instructions for spaCy are available [from spacy.io](https://spacy.io/docs/usage/).  In short, once Python is installed on your system:
    ```{bash, eval = FALSE}
    pip install -U spacy
    python -m spacy download en
    ```

    You can test your installation at the command line using:  

    ```{bash, eval = FALSE}
    python -c "import spacy; spacy.load('en'); print('OK')"
    ```
    
    Additional instructions are available from the spaCy website for installing using a [`virtualenv`](https://spacy.io/docs/usage/#pip) or an [Anaconda](https://spacy.io/docs/usage/#conda) installation. 
    
4.  Install the **spacyr** R package:

    To install the latest package from source, you can simply run the following.
    
    ```{r, eval = FALSE}
    devtools::install_github("kbenoit/spacyr", build_vignettes = FALSE)
    ```
    
    **Coming soon**:  Installation from CRAN will be possible using standard methods.

## <a name="multiplepythons"></a>Multiple Python executables in your system 

If you have multiple Python executables in your systems (for instance if you are a macOS user and have installed Python 3, you will also have the system-installed Python 2.7.x), then the `spacy_initialize()` function will check whether each of them have spaCy installed or not.  
You can also specify the python executable directly, when calling `spacy_initialize()`.  For instance, if your installation of spaCy uses `/usr/local/bin/python`, then you could use:
```{r, eval = FALSE}
library(spacyr)
spacy_initialize(python_executable = "/usr/local/bin/python")
```

## Comments and feedback

We welcome your comments and feedback.  Please file issues on the [issues](https://github.com/kbenoit/spacyr/issues) page, and/or send us comments at kbenoit@lse.ac.uk and A.Matsuo@lse.ac.uk.

## A walkthrough of **spacyr**

### Starting a **spacyr** session

To allow R to access the underlying Python functionality, it must open a connection by being initialized within your R session.  

We provide a function for this, `spacy_initialize()`, which attempts to make this process as painless as possible by searching your system for Python executables, and testing which have spaCy installed.  For power users (such as those with multiple installations of Python), it is possible to specify the path manually through the `python_executable` argument, which also makes initialization faster.

```{r}
require(spacyr)
spacy_initialize()
```

### Tokenizing and tagging texts

The `spacy_parse()` is **spacyr**'s main function.  It calls spaCy both to tokenize and tag the texts.  It provides two options for part of speech tagging, plus options to return word lemmas, entity recognition, and dependency parsing.  It returns a `data.frame` corresponding to the emerging [*text interchange format*](https://github.com/ropensci/tif) for token data.frames. 

The approach to tokenizing taken by spaCy is inclusive: it includes all tokens without restrictions, including punctuation characters and symbols.

Example:
```{r}
txt <- c(d1 = "spaCy excels at large-scale information extraction tasks.",
         d2 = "Mr. Smith goes to North Carolina.")

# process documents and obtain a data.table
parsedtxt <- spacy_parse(txt)
parsedtxt
```

Two fields are available for part-of-speech tags.  The `pos` field returned is the [Universal tagset for parts-of-speech](http://universaldependencies.org/u/pos/all.html), a general scheme that most users will find serves their needs, and also that provides equivalencies across langages.   **spacyr** also provides a more detailed tagset, defined in each spaCy language model.  For English, this is the [OntoNotes 5 version of the Penn Treebank tag set](https://spacy.io/docs/usage/pos-tagging#pos-tagging-english).
```{r}
spacy_parse(txt, tag = TRUE, entity = FALSE, lemma = FALSE)
```

For the German language model, the Universal tagset (`pos`) remains the same, but the detailed tagset (`tag`) is the [TIGER Treebank](https://spacy.io/docs/usage/pos-tagging#pos-tagging-german) scheme.


### Extracting entities

**spacyr** can extract entities, either named or ["extended"](https://spacy.io/docs/usage/entity-recognition#entity-types).
```{r}
parsedtxt <- spacy_parse(txt, lemma = FALSE)
entity_extract(parsedtxt)
```

```{r}
entity_extract(parsedtxt, type = "all")
```

Or, convert multi-word entities into single "tokens":
```{r}
entity_consolidate(parsedtxt)
```


### Dependency parsing

Detailed parsing of syntactic dependencies is possible with the `dependency = TRUE` option:
```{r}
spacy_parse(txt, dependency = TRUE, lemma = FALSE, pos = FALSE)
```


### Using other language models

By default, **spacyr** loads an English language model in spacy, but you also can load a German language model (or others) instead by specifying `model` option when calling `spacy_initialize()`. 

```{r}
## first finalize the spacy if it's loaded
spacy_finalize()
spacy_initialize(model = "de")

txt_german <- c(R = "R ist eine freie Programmiersprache für statistische Berechnungen und Grafiken. Sie wurde von Statistikern für Anwender mit statistischen Aufgaben entwickelt.",
               python = "Python ist eine universelle, üblicherweise interpretierte höhere Programmiersprache. Sie will einen gut lesbaren, knappen Programmierstil fördern.")
results_german <- spacy_parse(txt_german, dependency = TRUE, lemma = FALSE, tag = TRUE)
results_german
```
Note that the additional language models must first be installed in spaCy.  The German language model can be installed (`python -m spacy download de`) before you call `spacy_initialize()`.

### When you finish

A background process of spaCy is initiated when you ran `spacy_initialize()`. Because of the size of language models of spaCy, this takes up a lot of memory (typically 1.5GB). When you do not need the Python connection any longer, you can finalize the python connection (and terminate the process) by calling the `spacy_finalize()` function.

```{r, eval = FALSE}
spacy_finalize()
```
By calling `spacy_initialize()` again, you can restart the backend spaCy.


## Using **spacyr** with other packages

### **quanteda**

Some of the token- and type-related standard methods from [**quanteda**](http://githiub.com/kbenoit/quanteda) also work on the new tagged token objects:
```{r}
require(quanteda, warn.conflicts = FALSE, quietly = TRUE)
docnames(parsedtxt)
ndoc(parsedtxt)
ntoken(parsedtxt)
ntype(parsedtxt)
```

### Conformity to the *Text Interchange Format*

The [Text Interchange Format](https://github.com/ropensci/tif) is an emerging standard structure for text package objects in R, such as corpus and token objects.  `spacy_initialize()` can take a TIF corpus data.frame or character object as a valid input.  Moreover, the data.frames returned by `spacy_parse()` and `entity_consolidate()` conform to the TIF tokens standard for data.frame tokens objects.  This will make it easier to use with any text analysis package for R that works with TIF standard objects.


