---
output:
  md_document:
    variant: markdown_github
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

## Tips for Mac OS X Users

### Before install spaCy

You need to have a C++ complier, Xtools.  Either get the full Xcode from the App Store, or install the command-line Xtools using this command from the Terminal:
    
```{bash, eval = FALSE}
xcode-select --install
```

### Install spaCy and spacyr on Mac OSX

This document describes three methods to install spaCy and spacyr in the system.
1. use Python 2 from the homebrew package manager 
2. use Python 3 from the homebrew package manager 
3. use system default python. 

#### Install spaCy using homebrew python 2

Homebrew is a package manager for Mac OS X. You can install spaCy on it.

1. Install homebrew
    ```{bash, eval = FALSE}
    /usr/bin/ruby -e "$(curl -fsSL https://raw.githubusercontent.com/Homebrew/install/master/install)"
    ```
2. Install Python 2
    ```{bash, eval = FALSE}
    brew install python
    ```
3. Check if the default python is changed
    ```{bash, eval = FALSE}
    which python
    ```
    The output should be now `/usr/local/bin/python`
4. Setup pip
    ```{bash, eval = FALSE}
    pip install --upgrade setuptools
    pip install --upgrade pip
    ```
5. Install spaCy
    ```{bash, eval = FALSE}
    pip install -U spacy
    ```

6. Install the English language model
    ```{bash, eval = FALSE}
    python -m spacy download en
    ```
7. Check if the installation succeeded 
    ```{bash, eval = FALSE}
    python -c "import spacy; spacy.load('en'); print('OK')"
    ```
8. Install spacyr
    ```{r, eval = FALSE}
    devtools::install_github("kbenoit/spacyr")
    ```

If you are using a brew Python 2, the `spacy_initialize` is 
```{R, eval = FALSE}
library(spacyr)
spacy_initialize(use_python = "/usr/local/bin/python")
```

#### Install spaCy using homebrew python 3

1. Install homebrew
    ```{bash, eval = FALSE}
    /usr/bin/ruby -e "$(curl -fsSL https://raw.githubusercontent.com/Homebrew/install/master/install)"
    ```
2. Install Python 3
    ```{bash, eval = FALSE}
    brew install python3
    ```
3. Check the path for Python 3
    ```{bash, eval = FALSE}
    which python3
    ```
    The output should be now `/usr/local/bin/python3`
4. Setup pip3
    ```{bash, eval = FALSE}
    pip3 install --upgrade setuptools
    pip3 install --upgrade pip3
    ```
5. Install spaCy
    ```{bash, eval = FALSE}
    pip3 install -U spacy
    ```

6. Install the English language model
    ```{bash, eval = FALSE}
    python3 -m spacy download en
    ```
7. Check if the installation succeeded 
    ```{bash, eval = FALSE}
    python3 -c "import spacy; spacy.load('en'); print('OK')"
    ```
8. Install spacyr
    ```{r, eval = FALSE}
    devtools::install_github("kbenoit/spacyr")
    ```


If you are using a brew Python 2, the `spacy_initialize` is 
```{R, eval = FALSE}
library(spacyr)
spacy_initialize(use_python = "/usr/local/bin/python3")
```


#### Install spaCy on default Python (not really recommend)

Mac OS X comes with Python. In order to install spacy in that python, follow the steps below:

1. Install `pip`
    ```{bash, eval = FALSE}
    sudo easy_install pip
    ```
2. Install `spacy`
    ```{bash, eval = FALSE}
    sudo pip install spacy
    ```
3. Install the English language model
    ```{bash, eval = FALSE}
    python -m spacy download en
    ```
4. Check if the installation succeeded 
    ```{bash, eval = FALSE}
    python -c "import spacy; spacy.load('en'); print('OK')"
    ```
5. Install spacyr
    ```{r, eval = FALSE}
    devtools::install_github("kbenoit/spacyr")
    ```

If the default Python is used the initializaiton is simply:
```{R, eval = FALSE}
library(spacyr)
spacy_initialize()
```

