---
output:
  md_document:
    variant: markdown_github
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

## Tips for Windows Users

### Installing spaCy and **spacyr** in Microsoft Windows

#### Install spaCy

Installing spaCy in Windows is a bit complicated, but followings are the steps which we have been sucessful most of times.

1. Install python 3.\*. Although spaCy is supposed to work with 2.7.\*, there seems to be numerous problems installing the language modules with this setup.  Consequently, we strongly recommend using **Python 3** (currently 3.6.1). A Python 3 installer is avaialable at the [Python Official Page](https://www.python.org/downloads/release/python-361/).  The 64-bit version is recommended ("Windows x86-64 executable installer").
    * During the installation process, be sure to scroll down in the installation option window and find the "Add Python.exe to Path", and click on the small red "x." 

2.  A C++ compiler must be installed on your system. For Python 3 in windows, Virtual Studio Express 2015 should be installed (although Virtual Studio Express 2017 in recent releases covers Python 3, compilation of spaCy failed in our test). The current download link is [here](https://www.visualstudio.com/post-download-vs/?sku=xdesk&clcid=0x409&telem=ga#)

3. Install spaCy with the **Administrator Command Line**. 
    1. The installation of spaCy requires administrator privileges, as it generates symbolic links outside the user folder. In order to start it you need to do:
        * (Windows 7) https://technet.microsoft.com/en-gb/library/cc947813(v=ws.10).aspx
            1. Click **Start**, click **All Programs**, and then **click Accessories**.
            2. Right-click **Command prompt**, and then click **Run as administrator**.
            3. If the User Account Control dialog box appears, confirm that the action it displays is what you want, and then click Continue.
        * (Windows 8 and 10) See https://www.howtogeek.com/194041/how-to-open-the-command-prompt-as-administrator-in-windows-8.1/.
        
            1. Right-click on the Start button in the lower-left corner of the screen
            2. Select the **Command Prompt (Admin)** option from the Power User menu.
    2. Install spaCy. In the administrator command prompot, enter
        ```{bash, eval = FALSE}
        pip3 install spacy
        ```
    3. Install the English language model using these commands
        ```{bash, eval = FALSE}
        python -m spacy download en
        ```

    4. Test your installation at the command line using:  

        ```{bash, eval = FALSE}
        python -c "import spacy; spacy.load('en'); print('OK')"
        ```
    There are alternative methods of installing spaCy, especially if you have installed a different Python (e.g. through Anaconda).  Full installation instructions are available from the [spaCy page](https://spacy.io/docs/usage/#source-windows).

#### Install **spacyr**

4.  Install the [Rtools](https://cran.r-project.org/bin/windows/Rtools/) software available from CRAN.

5.  Installing the **spacyr** R package:

    To install the package from source, you can simply run the following.

    ```{r, eval = FALSE}
    devtools::install_github("quanteda/spacyr", build_vignettes = FALSE)
    ```

### When you have more than one python in your system

Things can go wrong in many ways if you have more than one Python executable. To check type
```
where python
```
If this returns more than one line of output, you have more than one.  **spacyr** will attempt to find the version in which you have installed spaCy, but you can always override this as an explicit argument to `spacy_initialize()`.

#### Specify the Python path in **spacyr**

The python path is set when `spacy_initialize()` is called for the first time after `spacyr` package is attached. Here is the example to specify the path:

```{r, eval = FALSE}
library(spacyr)
spacy_initialize(python_executable = "C:\Users\***\AppData\Local\Programs\Python\Python36\python.exe")
```
(where `***` is replaced by your user name, as indicated from `where python`.)

The value of `python_executable` has to be set to one of the python executables returned from `where python`, in which you have also installed spaCy and a language model.

